---
title: "Activity 2 - Day 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Packages
```{r, warning= FALSE}
library(tidyverse)
library(tidymodels)
```


# Loading GGally 
```{r}
library(GGally)
```

# Loading the dataset from the URL
```{r}
hfi <- readr::read_csv("https://www.openintro.org/data/csv/hfi.csv")

hfi
```
# Task 4 Pairwise Relations
```{r, warning=FALSE}
hfi %>% 
  select(ends_with("_score")) %>% 
  ggpairs()
```
# Task 5 The multiple linear regression model

```{r}
m_hr_ef <- lm(pf_score ~ hf_score + ef_score, data = hfi)
tidy(m_hr_ef)
```

The equation which I can represent from the above values is $y = -1.464e-11 + 2.00e+00 * hf_score + (-1.0000e+00) * ef_score$

# Challenges 3-D Plots

To design the 3D scatter plot installing required library

```{r}
library(scatterplot3d)
```

```{r}
s3d <- scatterplot3d(hfi$hf_score, hfi$ef_score, box= FALSE, color = "steelblue")
```

# Filter year to 2006 and creating a new dataset
```{r}
hfi_2016 <- hfi %>% filter(year == 2016)

hfi_2016
```

# Fitting the overall model

```{r}
# review any visual patterns
hfi %>% 
  select(pf_score, pf_expression_influence, pf_expression_control) %>% 
  ggpairs()

#fit the mlr model
m_pf <- lm(pf_score ~ pf_expression_influence + pf_expression_control, data = hfi)
tidy(m_pf)
```
# Fitting the overall model with "hfi_2016"

```{r}
# review any visual patterns
hfi_2016 %>% 
  select(pf_score, pf_expression_influence, pf_expression_control) %>% 
  ggpairs()

#fit the mlr model
m_pf_2016 <- lm(pf_score ~ pf_expression_influence + pf_expression_control, data = hfi_2016)
tidy(m_pf_2016)
```
# Is there a relationship between the response and predictors?

```{r}
summary(m_pf)
```
# Is there a relationship between the response and predictors? for 2016

```{r}
summary(m_pf_2016)
```

```{r}
#obtain fitted values and residuals for 2016
m_pf_aug_2016 <- augment(m_pf_2016)

# plot fitted values and residuals
ggplot(data = m_pf_aug_2016, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  xlab("Fitted values") +
  ylab("Residuals")
```

```{r}
# obtain fitted values and residuals
m_pf_aug <- augment(m_pf)

# plot fitted values and residuals
ggplot(data = m_pf_aug, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  xlab("Fitted values") +
  ylab("Residuals")
```


In my opinion, i could say that there is no linearity pattern witnessed from the above plot. Eventually, I can say that __high linearity__ between those two variables.



```{r}
ggplot(data = m_pf_aug_2016, aes(x = .resid)) +
  geom_histogram(binwidth = 0.25) +
  xlab("Residuals")
```

```{r}
ggplot(data = m_pf_aug, aes(x = .resid)) +
  geom_histogram(binwidth = 0.25) +
  xlab("Residuals")
```

```{r}
s3d <- scatterplot3d(hfi_2016$hf_score, hfi_2016$ef_score, box= FALSE, color = "red", grid= FALSE,
                     type = "h")
model <- lm(hfi_2016$pf_score ~ hfi_2016$pf_expression_influence + hfi_2016$pf_expression_control)
s3d$plane3d(model)
s3d$points3d(seq(10, 20, 2), seq(85, 60, -5), seq(60, 10, -10),
col = "red", type = "h", pch = 8)
```

